{\bf Stateless Model Checking \\ with Data-Race Preemption Points}

### 2016-03-01 oopsla/calcm.tex
write calcm conclusions slide

\begin{frame}{MC State of the Art}
	Modern stateless MC tools can {\em mitigate} exponential explosion.
	\begin{itemize}
		\item Dynamic Partial Order Reduction (DPOR)\related{Flanagan '05}
		\item State space estimation\related{Simsa '12}
	\end{itemize}
	\linegap

@@

\begin{frame}{Iterative Deepening}
	If time allows, combine PPs into larger, more comprehensive state spaces, eventually converging to using all PPs at once ({\em ``maximal'' state space}).
	\begin{center}
		\includegraphics[width=0.8\textwidth]{tree3.pdf}
	\end{center}
	% say: and depending on your time budget, you might decide that you expect this one to be feasible, or you might fall back to a smaller state space from before.
\end{frame}

\begin{frame}{Total Verification}
	% Let's come back to this issue of ...
	MC can {\em totally verify} a test by testing a state space with all possible PPs.
	\begin{itemize}
		\item Ordinarily infeasible, but some tests are small enough
		\item Whether a test can be totally verified can't be known in advance.
		\item ``Hard-coded'' PP approach\related{Musuvathi '08} sacrifices this possibility.
	%One downside of hard-coding PPs in advance is timing out when the test is too large, but another downside is if the test is small enough, you might miss a possible full verification!
		\item What PP strategy works for both small and large tests?
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Experimental Setup}
	\textbf{Test suite}: 79 ``P2''s $\times$ 6 test cases + 78 ``Pintos''s $\times$ 3 test cases
	\begin{itemize}
		\item P2: CMU 15-410 thread library project (\textasciitilde{}1800 LOC)
		\item Pintos: Berkeley CS162/U. Chicago CS320 kernel project (\textasciitilde{}700 LOC)
		\item 629 unique state spaces (i.e., project/test pairs)
	\end{itemize}
	\pause
	\linegap

	{\bf Quicksand experiment}: 1 hour $\times$ 10 CPUs per test
	\begin{itemize}
		\item {\bf QS}: Data-race PPs enabled
		\item {\bf QS-no-DRs}: Restrict iterative deepening to sync API PPs only
	\end{itemize}
	\linegap

@@

@@

\section{End}
\breakslide{\Large Questions?
\linegap

>>>>

\begin{frame}{MC State of the Art}{(my new DJ name?)}
	Modern stateless MC tools can {\em mitigate} exponential explosion.
	\begin{itemize}
		\item Dynamic Partial Order Reduction (DPOR)\related{Flanagan '05}
		\item State space estimation\related{Simsa '12}
	\end{itemize}
	\linegap

@@

\begin{frame}{Iterative Deepening}
	If time allows, combine PPs into larger, more comprehensive state spaces.
	\linegap

	All PPs enabled = ``maximal'' state space
	\begin{itemize}
		\item Prior work tools test this state space only.
	\end{itemize}
	%eventually converging to using all PPs at once ({\em ``maximal'' state space}).
	\begin{center}
		\includegraphics[width=0.8\textwidth]{tree3.pdf}
	\end{center}
	% say: and depending on your time budget, you might decide that you expect this one to be feasible, or you might fall back to a smaller state space from before.
\end{frame}

\begin{frame}{Total Verification}
	% Let's come back to this issue of ...
	MC can {\em totally verify} a test by testing a state space with all possible PPs.
	\begin{itemize}
		\item Ordinarily infeasible, but some tests are small enough
		%\item Whether a test can be totally verified can't be known in advance.
		\item ``Hard-coded'' PP approach\related{Musuvathi '08} sacrifices this possibility.
	%One downside of hard-coding PPs in advance is timing out when the test is too large, but another downside is if the test is small enough, you might miss a possible full verification!
		\item What PP strategy works for both small and large tests?
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Experimental Setup}
	\textbf{Test suite}: 79 ``P2''s $\times$ 6 test cases + 78 ``Pintos''s $\times$ 3 test cases
	\begin{itemize}
		\item P2: CMU 15-410 thread library project (\textasciitilde{}1800 LOC)
		\item Pintos: Berkeley CS162/U. Chicago CS320 kernel project (\textasciitilde{}700 LOC)
		\item 629 unique state spaces (i.e., project/test pairs)
	\end{itemize}
\end{frame}
\begin{frame}{Experimental Setup}
	\textbf{Quicksand experiment}: 1 hour $\times$ 10 CPUs per test
	\begin{itemize}
		\item {\bf QS}: Data-race PPs enabled
		\item {\bf QS-no-DRs}: Restrict iterative deepening to sync API PPs only
	\end{itemize}
	\linegap

@@

\begin{frame}{1. Finding more bugs with data-race PPs}
\end{frame}

\begin{frame}{2. Finding the same bugs... slower}
\end{frame}

\begin{frame}{3. Nondeterministic data-race candidates}
\end{frame}

\begin{frame}{4. Total verification}
\end{frame}

@@

\section{End}
\breakslide{\Huge Conclusion}

\begin{frame}{Conclusion}
	Stateless Model Checking depends on good {\bf preemption points} (PPs).
	\linegap

	MC State of the Art chooses a fixed PP set in advance.
	\linegap

	Quicksand schedules multiple tests, with different PPs, in parallel.
	\begin{itemize}
		\item Iterative Deepening incorporates new data-race PPs on-the-fly
		\item Data race PPs uncover {\bf 80\% more bugs} than sync API PPs alone
		\item Data race PPs enable {\bf total verification} when test is small enough
	\end{itemize}
	\linegap

	OOPSLA submission soon; looking for feedback!
\end{frame}

\breakslide{\Large Questions?
\linegap
